
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initialize data

```{r warning=FALSE}
if (!file.exists("2010_sqf_m35.csv")) {
  download.file("http://math.hmc.edu/m35f/2010_sqf_m35.csv", "2010_sqf_m35.csv")
}
if (!file.exists("2015_sqf_m35.csv")) {
  download.file("http://math.hmc.edu/m35f/2015_sqf_m35.csv", "2015_sqf_m35.csv")
}
sqf2010 <- read.csv("2010_sqf_m35.csv")
sqf2015 <- read.csv("2015_sqf_m35.csv")
sqf2015 <- sqf2015[!sqf2015$perstop == "*" && !sqf2015$perstop == " ",]
sqf2015$perstop <- as.numeric(as.character(sqf2015$perstop))
```

## Part i

```{r}
v <- t.test(sqf2010$perobs[sqf2010$haircolr == "BLACK"],
       sqf2010$perobs[sqf2010$haircolr == "BLOND"],
       alternative = "two.sided",
       mu = 0,
       paired = FALSE,
       var.equal = TRUE,
       conf.level = 0.95)
print(v)
```

The null hypothesis is that there is no difference between the period of observation in those with black hair and those with blond hair ($ \mu_{black} - \mu_{blond} = 0 $). Therefore the null value is zero.

The alternative hypotheis is that there is a difference between the period of observation in those with black hair and those with blond hair ($ \mu_{black} - \mu_{blond} \neq 0 $).

The alpha value is 1 minus the confidence level of 95%, so it is 0.05. We reject the null hypothesis if the p-value is less than or equal to alpha, and we fail to reject the null hypothesis if the p-value is greater than alpha.

From the t-test we have a p-value of `r v$p.value`, which is less than the alpha of 0.05, therefore we reject the null hypothesis and conclude that there is a difference between the period of observation in those with black hair and those with blond hair.

Furthermore, we are 95% confident that the true difference of period of observation in those with black hair and those with blond hair is between `r v$conf.int[1]` and `r v$conf.int[2]`.
