---
title: "StatsProject"
author: "Bowen Jiang"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = TRUE)
```

##  Comparison between 2010 and 2015

1. Data Preprocessing

```{r}
sqf2010=read.csv("2010_sqf_m35.csv")
sqf2015=read.csv("2015_sqf_m35.csv")

sqf2015=sqf2015[!sqf2015$perstop=="**" & !sqf2015$perstop==" ",]
sqf2015$perstop=as.numeric(as.character(sqf2015$perstop))
sqf2010$perstop = as.numeric(as.character(sqf2010$perstop))
```


2.  Overview

We are mainly interested in how the composition of people arrested changes between 2010 and 2015, espeically in terms of races.

We can first look at some basic information of the two years.

The number of people who got arrested in 2010 is,

```{r}
arst2010=sqf2010$arstmade
sum(arst2010)
```

Out of a population size of

```{r}
length(arst2010)
```

Therefore, the percentage of arrest is around 6.83\%

```{r}
sum(arst2010)/length(arst2010)
```

Similarly, for 2015,

```{r}
arst2015=sqf2015$arstmade
sum(arst2015)
length(arst2015)
sum(arst2015)/length(arst2015)
```

We have 3936 people who got arrested out of 22502, the arrest rate is around 17.49\%

3.

We can then look at the breakdown of arrested population in race.

In 2010, we have,

```{r}
counts2010=table(sqf2010$arstmade,sqf2010$race)
counts2010
barplot(counts2010)
```


we can also convert the data into percentage

```{r}
perc2010=prop.table(counts2010,2)
perc2010
```

then we have a percentage of arrested for each race,

American Indian/Alaskan Native: 4.89\%

Asian/Parcific Islander: 6.69\%

Black:  6.83\%

Black-hispanic: 7.83\%

Other: 5.57\%

Unknown:  6.39\%

White: 6.75\%

White-hispanic: 6.80\%

which we can also plot on a barplot,

```{r}
barplot(perc2010)
```

similarly, we calculate the statistics of 2015,

```{r}
counts2015=table(sqf2015$arstmade,sqf2015$race)
counts2015
barplot(counts2015)
perc2015=prop.table(counts2015,2)
perc2015
barplot(perc2015)
```

To visualize the difference, we put the two bar plots of percentage together,

```{r}
par(mfrow=c(1,2))
barplot(perc2010)
barplot(perc2015)
par(mfrow=c(1,2))
```

For year 2010, the race that is most likely to be arrested is black-hispanic, and it stays the same for year 2015.



